%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0.1,0.45,0.980}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Akim Khalitov} \\[7.5pt]
\href{https://t.me/akim1995}{\raisebox{-0.05\height}\faTelegram\ @akim1995}  \ $|$ \ 
\href{skype:live:akim.khalitov}{\raisebox{-0.05\height}\faSkype\ akim.khalitov} \ $|$ \ 
\href{https://www.linkedin.com/in/akim-khalitov}{\raisebox{-0.05\height}\faLinkedin\ akim-khalitov} \ $|$ \ 
\href{https://akim1995.github.io}{\raisebox{-0.05\height}\faGlobe \ akim1995.github.io} \ $|$ \ 
\href{mailto:akim.khalitov.@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ akim.khalitov.ya@gmail.com} \\ 
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}

Full Stack Developer with 5+ years of web development experience, specializing in JavaScript, Node.js, and PostgreSQL. Proficient in frontend frameworks: Vue.js, Angular, React. I fully embrace functional programming principles to enhance codebases' reliability and maintainability. \\
I speak Russian (native) and English.
%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{H4 Customized Software Zrt.} & \hfill Apr 2023 - Present (Remote) \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Full Stack developer (Java, JavaScript, React, PostgreSQL, Azure)}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{KL TECH} & \hfill Apr 2022 - May 2023 · 1 yr 2 mo \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Full Stack developer (Node.js, Javascript, TypeScript, React, Vue, PostgreSQL)}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Konig Labs} & \hfill May 2020 - May 2023 · 3 yrs 1 mo \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Front End developer and on later stages Full Stack (Javascript, TypeScript, React, Angular, Vue)}  \\
\end{tabularx}

% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{Designation} & \hfill Mar 2019 - Jan 2021 \\[3.75pt]
% \multicolumn{2}{@{}X@{}}{
% \begin{minipage}[t]{\linewidth}
%     \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
%         \item[--] long long line of blah blah that will wrap when the table fills the column width
%         \item[--] again, long long line of blah blah that will wrap when the table fills the column width but this time even more long long line of blah blah. again, long long line of blah blah that will wrap when the table fills the column width but this time even more long long line of blah blah
%     \end{itemize}
%     \end{minipage}
% }
% \end{tabularx}

%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{ADOAgregation} \\
\multicolumn{2}{@{}X@{}}{
Role: Full Stack developer \newline
The project involved the development of a suite of applications and Azure DevOps extensions aimed at consolidating disparate data from Volkswagen A.G branches and sub-contractors into a unified system within the Microsoft Azure infrastructure. It encompassed modules for data collection, transformation, and bidirectional synchronization from sources such as Jira, Azure DevOps cloud instances, Azure DevOps Repos, Azure DevOps Boards, and custom systems integrated with Azure DevOps. Additionally, the project involved coordinating and providing technical assistance to the data engineering team for efficient management and integration of data across systems. \newline
Technologies used: Azure, Node.js, Nest.js, React}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Students} \\
\multicolumn{2}{@{}X@{}}{
Role: Lead Frontend Developer \newline
The one-of-the-largest-university-in-the-country platform for the digitalization of work processes with students. Within the platform framework, the tasks of students signing in, planning, booking and paying for accommodation were solved. \newline
Technologies used: Angular 11, ngx-zorro, openapi-generator, TypeScript, GitLab, CI/CD}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{GesundenPlaner} \\
\multicolumn{2}{@{}X@{}}{
Role: Full Stack developer \newline
Service for the selection of exercises for the physical diagnosis and treatment of musculoskeletal system diseases.Admin panel implementation, RestAPI implementation for mobile applications, and Web interface. Role models, algorithms for selecting exercise programs for patients, user profiles, authorization, registration, and the entire backend were implemented. \newline
Technologies used: Node.js Nest.js, TypeScript, PostgreSQL, Cloudinary, Sendgrid, Azure, Devops, Angular11}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Trans Starter} \\
\multicolumn{2}{@{}X@{}}{
Role: Frontend Developer / Partly Backend Developer \newline
This project involved a comprehensive revamp of an eCommerce site, transitioning from PHP CMS to Vue.js and Nuxt.js with SSR. It featured custom components and a separate landing app heavily utilizing Vue-built web components. Yandex Maps was integrated for informational purposes. The back-end was modernized with a new C\# REST API, improving system efficiency. Additionally, an Elasticsearch engine was incorporated, providing fast and efficient search functionality, enhancing the overall user experience.\newline
Technologies used: Vue, Nuxt, SSR, TypeScript, PHP, C\#, Nginx, Microsoft SQL Server, Webcomponents, Yandex Maps, Elasticsearch, Azure}
\end{tabularx}

% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{Some Project} & \hfill \href{https://some-link.com}{Link to Demo} \\[3.75pt]
% \multicolumn{2}{@{}X@{}}{long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width}  \\
% \end{tabularx}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Daily Work Expertise: &  \normalsize{JavaScript, TypeScript, Node.js, Nest.js, PostgreSQL, Vue.js, React, Linux, Docker}\\
Secondary Skill Set:  &  \normalsize{C, Haskell, Elm, Clojure}\\  
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
